### 2017-11-04 monograph/thesis/chapters/introduction.tex
Remodeled the introduction.tex goals section and removed invalid
informations.

    Establish relationships between good programming practices and efficiency in
    programming, in addition to a new tool to support programmers in order to
    automate the long and diverse programming process in teams of developers
    with different programming `best practices'. \cite{pushdownAutomata}

@@

    \begin{enumerate}
        \item A study on universal programming tools, which from a single
        software, to work well behaved across all programming languages.
        Moreover, explain the differences for other softwares and the benefits
        of a unique tool, instead of several heavily different ones.

@@

        \item A study on the variety of existing tools for the support of good
        programming practices, beyond a comparative analysis between them,
        determining their weaknesses and strengths.

@@

        \item Propose a unique tool that allowing several and distinct
        programming `best practices' being implemented in several programming
        languages, which can be configured and set accordingly to their wishes.
    \end{enumerate}

    \section{Search Method}

    The work will be based on research in articles, books, theses,
    dissertations, trusted authors websites, and through new demonstrated
    evidences based on arguments in the monograph evolution road. Also, present
    results after building a new tool which proposes a solution for the problems
    presented and detailed. \cite{aspectOriented}

    In this proposal last chapter which lies in the topic
    \autoref{sec:implementation}, there is a series of weblinks and references
    preselected and may be used in the release build of this work. Noticing the
    texts of the last section probably will end up gradually moved to the first
    section of the text where there is the theoretical research, while
    correlated research are incorporated in the main written work.
    \cite{aspectOrientationReview}

    Moreover, at the end of the first part of this work, the completion of the
    subject entitled of Course Conclusion Work 1, leaving only the information
    for the implementation of the proposed tool to be implemented in the second
    part of this named thesis on \nameref{sec:implementation}.

>>>>

    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution road.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.

    In this proposal last chapter which lies on the part
    called `\nameref{sec:implementation}', which holds the implementation of a
    tool for code `Beautifying'.

@@

    \begin{enumerate}

        \item Establish relationships between good programming practices and efficiency in
        programming, in addition to a new tool to support programmers in order to
        automate the long and diverse programming process in teams of developers
        with different programming `best practices'.

@@

@@

        \item Discourse on the variety of existing tools for the support of good
        programming practices, with a comparative analysis between them,
        determining their weaknesses and strengths.

    \end{enumerate}

    \section{Implementation Goals}

    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.

    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.
